Append_smoothed_results

### 2017-01-04 Code/append_smoothed_results.Rmd

BlackWhite <- BlackWhite3
rm(BlackWhite3, BlackSmooth, WhiteSmooth)

BlackWhite$Census_Region <- "South"
BlackWhite$Census_Region[BlackWhite$State2 %in% c("Iowa", "Kansas", "Minnesota", "Missouri", 
                                                 "Nebraska", "North Dakota", "South Dakota", 
                                                 "Illinois", "Indiana", "Michigan", "Ohio", 
                                                 "Wisconsin")] <- "Midwest"

@@

>>>>

BlackWhite <- BlackWhite3
rm(BlackWhite3, BlackSmooth, WhiteSmooth)
```

```{r add_Census_Region}
BlackWhite$Census_Region <- "South"
BlackWhite$Census_Region[BlackWhite$State2 %in% c("Iowa", "Kansas", "Minnesota", "Missouri", 
                                                 "Nebraska", "North Dakota", "South Dakota", 
                                                 "Illinois", "Indiana", "Michigan", "Ohio", 
                                                 "Wisconsin")] <- "Midwest"

@@

```{r addvar_State_abbreviation}
BlackWhite <- BlackWhite %>% mutate(stabbrs = factor(State2,  
                                      labels = c("AL", "AK", "AZ", "AR", "CA", "CO", "CT", "DE", "DC",
                                                 "FL", "GA", "HI", "ID", "IL", "IN", "IA", "KS", "KY", 
                                                 "LA", "ME", "MD", "MA", "MI", "MN", "MS", "MO", "MT", 
                                                 "NE", "NV", "NH", "NJ", "NM", "NY", "NC", "ND", "OH", 
                                                 "OK", "OR", "PA", "RI", "SC", "SD", "TN", "TX", "UT", 
                                                 "VT", "VA", "WA", "WV", "WI", "WY")))

```
